Practical implications of HATEOAS on a bridge between LOD and SPARQL

### 2012-02-27 eswc-2012/workshop.tex
add timbl quote
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@120 43ef1190-90fd-4dd7-a769-d0121f02b80e

The LOD Cloud consists of well-linked datasets and to find simple
answers by simply dereferencing URIs, parse the returned content and
address it by conventional methods provided by the programming
language of choice, and this pattern has proved very useful. However,
for slightly more complex applications, one has to traverse a
relatively large graph to find the data one requires. In most cases,
one would need to match the graph with a pattern, which is essentially
what the SPARQL query language does. The main problem is that there
may not be a link present that makes it possible for the application
to find the query endpoint without requiring out-of-band information,
which implies that non-REST interactions are required. To remedy this
situation, we would need to add more links.

@@

\begin{enumerate}
\item TimBL suggests in the Linked Data Design
  Issue\footnote{\url{http://www.w3.org/DesignIssues/LinkedData}} the
  use of ``Minimum Spanning Graph'', what other triples would humans
  and machines find useful?

>>>>

The LOD Cloud consists of well-linked datasets and to find simple
answers by simply dereferencing URIs, parse the returned content and
address it by conventional methods provided by the programming
language of choice, and this pattern has proved very useful. However,
for slightly more complex applications, one has to traverse a
relatively large graph to find the data one requires. In most cases,
one would need to match the graph with a pattern, which is essentially
what the SPARQL query language does. In the Linked Data Design
Issue\footnote{\url{http://www.w3.org/DesignIssues/LinkedData}} Tim
Berners-Lee notes ``To make the data be effectively linked, someone
who only has the URI of something must be able to find their way the
SPARQL endpoint.'', but this is generally not possible today without
requiring out-of-band information, which implies that non-REST
interactions are required. To remedy this situation, we would need to
add more links.

@@

\begin{enumerate}
\item Tim Berners-Lee suggests in the Linked Data Design
  Issue\footnote{\url{http://www.w3.org/DesignIssues/LinkedData}} the
  use of ``Minimum Spanning Graph'', what other triples would humans
  and machines find useful?
